---
title: "Bird Age"
author: "Robin"
date: "August 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)

```

## Bird Age

I stumbled across a dataset of bird ages on a (USGS website)[https://www.pwrc.usgs.gov/bbl/longevity/longevity_main.cfm], and wanted to know if there was a relationship between bird age and other variables (weight, wingspan, etc)


```{r load data}
birdage=read_csv("bird age.csv") %>% #this data is from https://www.pwrc.usgs.gov/bbl/longevity/longevity_main.cfm
 separate(., "Minimum age at encounter", into=c("year","year2","month","month2"), sep=" ") %>%
  filter(complete.cases(.)) %>% #I just chucked out one row because the bird age was less than a year, I'll figure out how to keep it later. Had to do this versus using the dates because the dates are screwed up (some say '99' for the day of the month)
  mutate(age=as.numeric(year)+(as.numeric(month)/12)) #so that we can factor in partial years
  
birdnames=read_csv("birdnames.csv")   #this data is from http://fielddata.blogspot.com/p/field-notes-data-tips-download-page.html
birdnameage=merge(birdage, birdnames, all=T) %>% #merge the two datasets together
filter(., !is.na(select(., age)))

gapnames=read_csv("gapnames.csv") #I manually found some on Wiki quickly, not sure theyre perfect to species
gapnames=gapnames[!duplicated(gapnames$COMMONNAME),] #maybe if I get rid of duplicates?

test=merge(birdnameage, gapnames, all =T) #I have no fucking clue why this isnt working ill fix this later

```

## Link Between Bird Age and Phylogenetic Order?

I wanted to know if there was any signal for how old birds get if theyre closely related. Ultimately, I would love to know how age is affected by size (weight, wingspan, whatever) but I cant find open datasets for that.

```{r histogram}
ggplot(birdnameage, aes(age))+
  geom_histogram()+
  theme_bw()

```




```{r }
ggplot(birdnameage, aes(Order, age))+
  geom_jitter()+
  geom_boxplot(aes(alpha=0.3),outlier.shape = NA)+
  theme(axis.text = element_text(angle=90, hjust = 1, size=10),
        legend.position = "none",
        axis.title=element_text(size=14, face = "bold"))
```

